Music Recommendation System Using the Million Song Dataset

### 2015-05-07 writeup/MSDgroupwriteup.tex
new pdf

\section{Notes}
Sparsity of $8.08199453451\times 10^{-5}$ (needs updating)

%The matrix was too big for our computers to handle the matrix factorization using the whole set of users and songs, so we subset the data. 
%Subset songs by how many times the song was listened to. i.e the popularity of the song
%= new number 
%Subset users by how many songs they've listened to (how many popular song?)
%= new number

29 - users
34 - songs 
60 \%

Interesting plots:
- Cumulative Distribution of number of songs with a given play count

To Reference a paper:

The Million Song Dataset Challenge: \citep{McFee:2012:MSD:2187980.2188222} \\
Million Song Dataset Recommendation Project Report: \citep{li2012million} \\
codebook-based scalable music tagging with poisson matrix factorization: \citep{liangcodebook} \\
Matrix Factorization Techniques for Recommender Systems: \citep{koren2009matrix} \\
A Preliminary Study on a Recommender System for the Million Songs Dataset Challenge: \citep{aiolli2013preliminary} \\

>>>>

%To Reference a paper:

%The Million Song Dataset Challenge: \citep{McFee:2012:MSD:2187980.2188222} \\
%Million Song Dataset Recommendation Project Report: \citep{li2012million} \\
%codebook-based scalable music tagging with poisson matrix factorization: \citep{liangcodebook} \\
%Matrix Factorization Techniques for Recommender Systems: \citep{koren2009matrix} \\
%A Preliminary Study on a Recommender System for the Million Songs Dataset Challenge: \citep{aiolli2013preliminary} \\
